Hypertension and microbiome

### 2019-04-29 articletwo.Rmd
Toggle sourced
Minor

### Officer functions

@@

# Loading data

@@

maaslinplot <- ggplot(maas.tables.df, aes(x = Feature, y = reorder(Name, my.plot.order(Name)), fill = beta)) +
    geom_tile(aes(fill = 1)) +
    geom_tile(colour="white", size=0.25) +
    scale_fill_distiller(palette = "RdBu", name = "Effect size",
                         limits=c(-0.003, 0.003), breaks = c(-0.003, 0, 0.003), na.value="grey30") +
    coord_fixed() +
    xlab("") +
    ylab("") +
    theme_classic(10) +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1.0, vjust=0.5, size=7),
          axis.text.y = element_text(size=7))

>>>>

<details>
  <summary>Toggle imported core</summary>
### Officer functions

@@

</details>
# Loading data

@@

maaslinplot <- ggplot(maas.tables.df, aes(x = Feature, y = reorder(Name, my.plot.order(Name)), fill = beta)) +
    geom_tile(aes(fill = 1)) +
    geom_tile(colour="white", size=0.25) +
    scale_fill_distiller(palette = "RdBu", name = "Effect size",
                         limits=c(-0.003, 0.003), breaks = c(-0.003, 0, 0.003), na.value="grey30") +
    coord_fixed() +
    xlab("") +
    ylab("") +
    theme_classic(10) +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1.0, vjust=0.5, size=10),
          axis.text.y = element_text(size=10))
